Enhancing Multiple Myeloma Cell Segmentation through Physical Image Transformations

### 2023-05-02 paper/paper.tex
Updated paper

While the individual physical image transformations showed results similar to the baseline model without any transformation, we believe that further improvement can be achieved by combining multiple transformations in an ensemble approach. This can help to address the limitations of each individual transformation and enhance the overall performance of the segmentation model.

In conclusion, our study demonstrates the potential of physical image transformations to improve the accuracy of Multiple Myeloma cell segmentation. These findings can contribute to the development of more effective and reliable segmentation models for the diagnosis and treatment of Myeloma.

>>>>

While the individual physical image transformations showed results similar to the baseline model without any transformation, we believe that further improvements can be achieved by combining multiple transformations in an ensemble approach. This may help to address the limitations of each individual transformation and enhance the overall performance of the segmentation model.

In conclusion, our study demonstrated the potential of physical image transformations to improve Multiple Myeloma cell segmentation. These findings can contribute to the development of more effective and reliable segmentation models for the diagnosis and treatment of Multiple Myeloma.
